### 2016-03-10 paper/introduction.tex

We have validated our ideas on three problems in Computer Vision,
stereo, optical flow, and layered depthmap estimation. \yasu{add more
once we see results.}  Our approach is extremely simple in concept, and
will instantly benefit every Computer Vision researcher or engineer, who
currently uses fusion move algorithm on multi-core environments to solve
challenging problems. We will share our implementation of the
algorithm. The rest of the paper is organized as
follows. Section~\ref{section:related_work}....

@@

%
 \yasu{Hopefully, more interesting things will come up through
experiments and we have more to say. For example, it would be cool if
uniform model is better than pure master-slave. Then we can write that
ours is not just parallel. But keeping multiple solutions somehow
benefit (GA/GP algorithm's ideas).}

@@

3. I would suggest removing "Genetic algorithms" from the paragraph heading at the end of section 2 or replacing it with "Evolutionary Algorithm".

4. We should cite two more papers
(a) Hierarchical Graph cuts (Kumar and Koller, UAI 2009)
(b) Making the right move (Batra and Kohli, CVPR 2010)

>>>>

We have evaluated our ideas on three problems in Computer Vision,
stereo, optical flow, and layered depthmap estimation. Our approach
outperforms all the other competing methods, especially for challenging
problems with a large label space.  Our approach is extremely simple in
concept, and is easily reproducible by standard Computer Vision engineers.
% will instantly benefit every Computer Vision researcher or
% engineer, who currently uses fusion move algorithm on multi-core
% environments to solve challenging problems.
% We will share our implementation of the algorithm.

@@

%
%  \yasu{Hopefully, more interesting things will come up through
% experiments and we have more to say. For example, it would be cool if
% uniform model is better than pure master-slave. Then we can write that
% ours is not just parallel. But keeping multiple solutions somehow
% benefit (GA/GP algorithm's ideas).}

@@

%3. I would suggest removing "Genetic algorithms" from the paragraph heading at the end of section 2 or replacing it with "Evolutionary Algorithm".

%4. We should cite two more paper

### 2016-03-10 paper/layered_depthmap.tex
yasu

Solution proposals depend heavily on the current solution, eliminating
the possibility of using hierarchical approach, which needs to enumerate
all the proposals to start. Therefore, the only viable competing method
is Parallel Fusion Move, that replaces constant label solutions by
solution proposals in parallel alpha-expansion framework. We will also
evaluate the standard Fusion Move method.
%
The fusions are binary, for which we use QPBO.

@@

\mysubsubsection{Swarm fusion architecture}
The three swarm architectures in Fig.~\ref{fig:model} are evaluated. The
fusions are multi-way, for which we use TRW-S.

>>>>

Solution proposals depend heavily on the current solution, eliminating
the possibility of using hierarchical approach, which needs to enumerate
all the proposals to start. Therefore, the only viable competing method
is Parallel Fusion Move as in the optical flow problem. We will also
evaluate the standard Fusion Move method.
%
The fusions are binary, for which we use QPBO.

@@

\mysubsubsection{Swarm fusion architectures}
The three swarm architectures in Fig.~\ref{fig:model} are evaluated.
The architecture parameters are exactly the same as in the optical flow problem:
$\alpha=2$ ($\beta=0$) in SFWSS, the iteration of
($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) in SFWMF, and
($\alpha=1, \beta=1$) for the standard SF.
%
The fusions are multi-way, for which we use TRW-S.

### 2016-03-10 paper/optical_flow.tex
yasu

We use Swarm fusion to solve an optical flow problem, where a baseline
is a FM-based algorithm by Lempitsky et al.~\cite{viktor_optical_flow}.
Although their paper did not consider parallel implementation, it is
straightfoward to apply the concept of parallel alpha-expansion and
construct a ``parallel fusion move'' method, where multiple threads
repeat fusing two solutions via QPBO. This time, we will compare it with
our full swarm fusion model (bottom right example in
Fig.~\ref{fig:model}).

>>>>

Fusion Move was first introduced by Lempitsky et al.~\cite{viktor} to
solve the optical flow problem.
%Optical flow was the problem, in which the Fusion Move method was first
%introduced by Lempitsky et al.~\cite{viktor}.
We copy their problem setting and proposal generation schemes for our
second problem.  We use test images in the Middlebury optical flow
benchmark~\cite{middlebury_optical_flow}.

\mysubsubsection{Competing methods} Fusion Move method in Lempitsky's
paper is the first natural contender. While they did not consider
parallel implementation, it is straightforward to combine the idea of
Parallel Alpha-Expansion and Fusion Move. Therefore, the second competing
method is ``Parallel Fusion Move (PFM)'', which is equivalent to
Parallel Alpha-Expansion with the constant label solutions replaced by
the solution proposals.
%each thread repeats generating
%a solution proposal and fusing it to the current solution. Solutions
%from all the results are sequentially fused to obtain the final solution
%as in the Parallel Alpha-Expansion method.
%
One problem of PFM is that infinite number of solution proposals can be
generated in their algorithm, and we do not know when we should stop and
perform the final sequential fusion. In our experiments, we manually
picked a time limit to initiate the final fusion.
%In Fig.~\ref{fig:model}, this computational framework corresponds to
%``parallel alpha-expansion'' with the label solutions replaced by
%solution proposals.
%
The last contender is the mix of the Hierarchical Fusion and the Fusion
Move method, dubbed ``Hierarchical Fusion Method'', where they start
from solution proposals as opposed to constant labels. One problem is
that we do not know how many solution proposals to generate to start
with. We have manually picked a good number (X \yasu{how many Hang?})
for the experiments.
%
The fusions are binary in these methods and we have used QPBO.

\mysubsubsection{Swarm fusion architectures}
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The three swarm architectures in Fig.~\ref{fig:model} (SFWSS, SFWMF, SF)
have been evaluated against the competing methods. Note that we have
used the same set of proposal generation schemes. The fusions are
multi-way, for which we have used TRW-S.
% The full swarm fusion model (at the bottom right in
% Fig.~\ref{fig:model}) will be used to evaluate the effectiveness of our
% method. We will also try the other two Swarm fusion variants in
% Fig.~\ref{fig:model} with restrictions.
We have chosen $\alpha=2$ ($\beta=0$) in SFWSS, the iteration of
($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) in SFWMF, and
($\alpha=1, \beta=1$) for the standard SF.  The fusions are multi-way,
for which we use TRW-S.

### 2016-03-10 paper/related_work.tex

\noindent Lempitsky et al. introduces parallel computation to an
alpha-expansion technique, where multiple threads simultaneously fuses
mutually exclusive sets of labels. Delong et al.~\cite{delong} and
Veksler~\cite{olga} proposed an hierarchical fusion algorithm, where
labels are simultaneously fused from the bottom to the top in a tree of
labels. Strictly speaking, these parallelize alpha-expansion and are not
in the family of Fusion Move methods, because they never generate
solution proposals. Our approach parallelize fusion move methods.

@@

\noindent
The core MAP inference algorithms themselves can be parallelized.
Strandmark et al. parallelized graph-cuts~\cite{strandmark2010parallel}.
%
Message passing algorithms are friendly to GPU implementation and can
exploit the power of parallel computation.
%
However, the core optimization libraries are often very complex and
require significant engineering by experts for modification.
%
While state-of-the-art optimization libraries are often freely available
for non-commercial purposes, most companies have to develop and maintain
in-house implementation of these algorithms. The modification of the
core optimization libraries is a significant engineering investment for
many companies. In contrast, our idea is extremely simple and instantly
reproducible by standard engineers.

@@

\noindent FM was first introduced by Lempitsky et al. in solving an
optical flow problem~\cite{first_fusion_viktor}. FM has been effectively
used to solve challenging problems in Computer Vision such as a stereo
problem with second order smoothness priors~\cite{woodford}, a stereo
problem with parameteric surface fitting and segmentation (i.e., Surface
Stereo)~\cite{surface_stereo}, or multicut
partitioning~\cite{fusionmovesforcorrelationclustering}.
%
FM has two main advantages over the other general inference
techniques~\cite{trw,loopy_belief_propagation}. First, FM allows us to
exploit domain-specific knowledge in customizing proposal generation
schemes. Second, FM can handle problems with very large label spaces
(and even real-values variables), because the core optimization just
solves a binary decision problem.

In contrast, methods like message passing algorithms need to maintain
messages and beliefs for the entire label space all the time.
%
Although conceptually straightforward, we are not aware of {\it parallel
fusion move} algorithms that fuses solution proposals, as opposed to
labels, in parallel. This paper seeks to fully unleash the power of
parallel computation in FM via more general framework.

>>>>

\noindent Lempitsky et al. introduces parallel computation to an
alpha-expansion technique, where multiple threads simultaneously fuses
mutually exclusive sets of labels. Kumar et
al.~\cite{hierarchical_graph_cuts_kumar_and_koller}, Delong et
al.~\cite{delong}, and Veksler~\cite{olga} proposed an hierarchical
approach, where labels can be simultaneously fused from the bottom to
the top in a tree of labels. 
% 
%Strictly speaking, these parallelize alpha-expansion approaches are not
%in the family of Fusion Move methods, because they never generate
%solution proposals. Our approach parallelize fusion move methods.
Instead of taking a hierarchical approach, Batra et
al.~\cite{Dhruv_pushmeet_making_the_right_move} adaptively computed an
effective sequence of labels to explore. This technique can be combined
with parallel alpha-expansion techniques to further obtain speed-up.

@@

\noindent
The core MAP inference algorithms themselves can be parallelized.
Strandmark et al. parallelized graph-cuts~\cite{strandmark2010parallel}.
%
Message passing algorithms are friendly to GPU implementation and can
exploit the power of parallel computation.
%
However, the core optimization libraries are often very complex and
require significant engineering by experts for modification.
%
While state-of-the-art optimization libraries are often freely available
for non-commercial purposes, most companies have to develop and maintain
in-house implementation of these algorithms. The modification of the
core optimization libraries is a significant engineering investment for
many companies. In contrast, our idea is extremely simple and easily
reproducible.

@@

\noindent FM was first introduced by Lempitsky et al. in solving an
optical flow problem~\cite{first_fusion_viktor}. FM has been effectively
used to solve challenging problems in Computer Vision such as a stereo
problem with second order smoothness priors~\cite{woodford}, a stereo
problem with parameteric surface fitting and segmentation (i.e., Surface
Stereo)~\cite{surface_stereo}, or multicut
partitioning~\cite{fusionmovesforcorrelationclustering}.
%
FM has two main advantages over the other general inference
techniques~\cite{trw,loopy_belief_propagation}. First, FM allows us to
exploit domain-specific knowledge in customizing proposal generation
schemes. Second, FM can handle problems with very large label spaces
(and even real-values variables), because the core optimization just
solves a binary decision problem.
%
In contrast, methods like message passing algorithms need to maintain
messages and beliefs for the entire label space all the time.
%
Although conceptually straightforward, we are not aware of {\it parallel
fusion move} algorithms that fuses solution proposals, as opposed to
labels, in parallel. This paper seeks to fully unleash the power of
parallel computation in FM via more general framework.
